---
title: "Sample R Training Exam"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: false
runtime: shiny_prerendered
---

```{r setup, include=FALSE, warning = FALSE}
library(learnr)
library(learnrhash)
library(magrittr)
tutorial_options(exercise.timelimit = 10,
                 exercise.startover = FALSE)

```


# Sample R Training Exam

I have set this exam to have a time limit of 10 minutes, but we can set it any way we want.  I included all the questions from the ADaM.yml file.  Currently there is no easy way to randomly sample these questions and include only a subset.  But, I don't think that's impossible either, I just need to think about how to do it. Total effort to create what you saw here was about an hour.  I also don't know yet how we will authenticate users this way, that's another thing to think about.

## Grading

At the very end there I've got a submit button that will generate a hash value of the responses for me to evaluate.  We should be able to set up some sort of automated system that would grade them on the back end.

There is also the `gradethis` package to grade the responses.  It is usually used for displaying helpful messages after someone submits a code chunk.  But I think we could hack it a bit to grade some multiple choice questions and then capture that and save it to the server.




## Code section

This could be a code section where we could include some SAS code and ask users to do something about it with R:

```bash
PROC PHREG DATA = DAT;
     CLASS VAR1 VAR2 VAR3;
     MODEL TIME*STATUS(0) = VAR1 VAR2 VAR3;
RUN;

```


```{r, phreg, echo = FALSE}
quiz(caption = "Refer to the SAS code above:",
     question("Which is the equivalent R function to `PROC PHREG`",
              answer("`survival::coxph()`", correct = TRUE),
              answer("`stats::glm()`"),
              answer("`stats::lm()`"),
              answer("`survival::survreg()`")))

```


## ADaM

You can use the programming window below as a scratch space to answer the questions if any of them needed a coding window.  None of these questions do, but here's an example:

```{r adam_box, exercise = TRUE}

```

```{r adam, echo = FALSE}
quiz(caption = "These are the quiz questions from AdaM.yml",
       question("Why is ADaM submitted as SAS Version 5 transport files?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
            answer("Because FDA standardized to this format in 1999.", correct = TRUE),
            answer("Because SAS is the only format that is usable by review software"), 
            answer("Because the ADaM team made this decision"),
            answer("Because other formats could confuse the reviewers")),
  
  question("Which of the following is not part of the goals and mission of ADaM?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
          answer("Support SAS software tools", correct = TRUE),
            answer("Support efficient generation, replication and review of analysis results", ),
            answer("Transparency, Traceability, and clear communication"),
            answer("Meet the needs of FDA Reviewers")),

  question("How does ADaM help FDA reviewers (select the best response)?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
       answer("Analysis data from all companies can be in the same structure"), 
       answer("Data can be combined across companies and by therapeutic areas"), 
       answer("Supports the larger vision of an FDA data repository"),
       answer("All of the above", correct = TRUE)),

  question("Which of the following is not a fundamental principle of ADaM?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
     answer("Includes all raw data", correct = TRUE),
       answer("Clear communication and traceability"),
       answer("Support efficient generation, replication and review of analysis results"),
       answer("Meet the needs of FDA Reviewers")),

  question("ADaM datasets are designed for what primary purpose?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
          answer("Production of primary efficacy and safety analyses that are specified in the statistical analysis plan", correct = TRUE),
       answer("Replication of all SDTM data with the addition of derived data"),
       answer("Exploratory analysis"),
       answer("Production of all statistical tables and listings")),

  question("What is the first step to take when deciding on the name for a derived variable in ADaM?",
                     allow_retry = FALSE,
                     random_answer_order = FALSE,
             answer("Study the ADaM implementation guide and determine if there is a variable name or fragment that is appropriate for the variable concept", correct = TRUE),
             answer("Use a variable name that is an abbreviation for the variable concept"),
             answer("Look for a variable name in the SDTM implementation guides that is a good fit for the variable concept"),
             answer("None of the above")),

  question("What is one of the two ways to achieve traceability?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
             answer("Informative metadata", correct = TRUE),
             answer("Double programming"),
             answer("A list of SDTM domains used for dataset creation"),
             answer("A diagram")),

  question("BDS differs from ADSL in that it allows which of the following?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
             answer("Multiple records per subject", correct = TRUE),
             answer("No treatment variables"),
             answer("One record per subject"),
             answer("Subject level data")),

  question("What is a possible reason for why the value of VISIT will differ from AVISIT for a given observation?",
                     allow_retry = FALSE,
                     random_answer_order = FALSE,
  answer("AVISIT can be a completely derived concept."),
  answer("AVISIT value may be based on windowing algorithm which results in a different visit window description than the nominal VISIT value."),
             answer("The text of AVISIT may more clearly define the timing of the visit than the text of VISIT. For example, AVISIT=“Month 3” and VISIT=“Visit 3”. "),
       answer("All of the above.", correct = TRUE)),

  question("Which of the following is the ADaM variable used to represent the treatment a subject actually received?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
       answer("TRTxxA", correct = TRUE),
       answer("TRTxxP"),
       answer("APxxSDT"), 
       answer("TRTSEQA"), 
       answer("ACTARM")),
  
  question("Which is the variable used to indicate whether a subject is included in the Intent-to-treat population?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
       answer("ITTFL", correct = TRUE),
       answer("INTENTFL"),
       answer("POPINTFL"), 
       answer("POPFLAG1")),

  question("What data set name should be used for the subject level analysis dataset?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
     answer("ADSL", correct = TRUE),
  answer("ADSUBJ"), 
  answer("SUBJLEV"), 
  answer("ADSL1")),

  question("Which of the following variables are required to be included in ADSL and copied directly from SDTM DM?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
     answer("AGE, SEX, AGEU, ARM", correct = TRUE),
     answer("DMDTC, AGE, RFSTDTC, ARM"), 
     answer("USUBJID, SITEID, AGEU, AGEGROUP"), 
     answer("ACTARM, ACTARMCD, ARM, ARMCD")),

  question("Which of the following pairs of variables are BOTH required for a BDS dataset?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
            answer("PARAM and PARAMCD", correct = TRUE),
            answer("PARAM and PARAMN"),
            answer("PARCATy and PARAMCD"), 
            answer("PARAMN and PARCATy")),

  question("Which group of variables must always be present in a BDS dataset?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
     answer("PARAM, PARAMCD, AVAL and/or AVALC", correct = TRUE),
       answer("PARAM, AVALCAT1, AVAL"), 
            answer("AVAL, BASE, SUBJID"), 
            answer("USUBJID, SAFFL, AVAL")),

  question("PARAM must meet which of the following criteria?",
                     allow_retry = FALSE,
                     random_answer_order = TRUE,
          answer("It must be a complete text description of the parameter.", correct = TRUE),
       answer("It must be a short code value of the parameter."), 
      answer("It must include information on covariates or other predictor variables."), 
      answer("All of the above.")))


```

<hr>

## Submission

In the example below a url is given, this value can be replaced with whatever link you would like to use for submission. This link would be a Shiny form, or maybe we could parameterize this document.  I'll think about it some more.


```{r context="server"}
learnrhash::encoder_logic()

```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(ui_before = learnrhash::default_ui(url = "https://www.r-consortium.org"))
```
